Insight Into Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-08-18 draft.tex
wrote first part of conclusion

\subsubsection{Concluding Remarks}
Except for gender in the age-plot, no variable could be explained with reasonable accuracy for age or body size.

@@

\section{\uppercase{Conclusion}}
\label{sec:Conclusion}

>>>>

@@

\section{\uppercase{Conclusion}}
\label{sec:Conclusion}
The presented results indicate that the parameters torsion, curvature and curvature angle are not enough to characterize pathological changes in the lumbar spine.
%%
They are well suited to characterize subject gender due to their height difference using mean curvature and mean curvature angle.
%%
The reason for this lies in the higher curvature of smaller subjects and the significant difference of average body size between males and females.
%%
Gender was characterized well in the analysis of all subjects as well as subjects divided by age.

Subjects grouped using body height have a similar spine shape and a lower variance.
%%
The remaining information within these groups is not enough to characterize back pain related variables.
%%
Certain subgroups, however, can be classified for various size groups, such as nutrition or psychological parameters.
%%

Another observation during the analysis are very large decision trees achieving low error scores.
%%
Their complexity however impose overfitting to the data and they are not suitable for extracting universal rules.

\subsection{Proposed Features}

\subsection{Applicability of the Method}

Except for gender in the age-plot, no variable could be explained with reasonable accuracy for age or body size.
\com{Vorgestellte Parameter nicht ausreichend.}
\com{Weitere Parameter wichtig - z.B. Dicke der Wirbelkoerper, Durchmesser des Spinalkanals, Form der gesamten Wirbelsaeule, Cobb-Winkel}
